\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-14 paper/draft.tex
Added ubuntu version and jalangi version

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
\newcommand{\rf}[1]{\ref{#1}}
\newcommand{\se}[1]{\S\ref{#1}}
\newcommand{\fg}[1]{Fig.~\ref{#1}}

\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

% FIXME:
\newcommand{\pc}{PIC\xspace}
\newcommand{\pcs}{\pc{}s\xspace}

@@

Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
  instead of simply locating and loading a library from the file-system, it yields control to \sys, which applies a series of transformations to libraries with the goal of interposing at their boundaries.
We start with an overview of dialysis~\sx{overview}, highlighting several key challenges, followed by a detailed description of each step~(\S\ref{one}--\ref{three}).

@@

% FIXME: add user data
At a high level, the goal of program dialysis is to dismantle the program at the boundaries of third-party libraries, apply transformations that insert analysis-specific machinery, and then carefully assemble individual components to maintain the original semantics.
 In more detail:

@@

% Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}. The meta-function $\alpha$ stands for the locations of analysis hooks.
  }
}
\label{fig:base}
\end{figure}

% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
% The following subsections detail these steps.

\subsection{Dismantling}
\label{one}

When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc

It then dynamically replaces the implementation of\ttt{import}:
  rather than simply locating and loading a library, the function yields to \sys.

\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
% \omit{---the common case---}
Otherwise, \sys first invokes the built-in library loader to locate the library.

The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
A series of transformations is applied before and after interpretation~\sx{two}.

Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
\sys must note not to include these constructs in the ones 
% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
  the key to remember is that analysis are loaded from disk as source files, similar to libraries.

@@

\subsection{Transformation}
\label{two}

For each analyzed library, \sys needs to place hooks all around its boundary---not just its interface.
This is achieved in three logical steps:
(i) transforming the variable context, a mapping from names to values, within which the library will be interpreted,
(ii) interpreting the library within this context, so that all names resolve to \sys-augmented values, and
(iii) transforming the return value, \ie the library interface, once the interpretation is complete.
Before discussing \emph{where} each transformation are applied, however, it makes sense to see \emph{how} they are applied.

\heading{Transformations}
% , such as an object returned from a module or an exception about to be sent across the network.
Transformations can be applied to any value in the language, which can generally be a primitive, a function, or a compound value---say, a list of values or an object of key-value pairs.
% Listing~\ref{core-tx} presents a simplified core of the language.
Transformations walk compound values from their root, processing component values based on their types (Fig.~\ref{fig:base}).
More specifically,
  (i) \emph{function} values are wrapped by closures that contain analysis-specific hooks; % on the function's arguments and return values;
  (ii) \emph{object} and \emph{list} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
To avoid cycles during the walk, values are added to map that is consulted at the beginning of each recursive call.
% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.

% \sys's transformations boil down to a base form \ttt{BT} that augments \emph{objects} with runtime security monitors.
% At a high level, \ttt{BT} takes an object $O$ and a \pc $\sigma$ and returns a new object $O'$.
% Every field $f$ of $O$ is wrapped with a method $f'$ defined to enclose $f$.
% At runtime, $f'$ checks $\sigma$:
%  if the access is allowed, it forwards the call to $f$;
%  otherwise, it raises an exception.
% % Appendix: An example result is shown in the appendix.~\ref{fig:bt2}.
% 
% To achieve this transformation, \sys walks the object graph from the root and processes component values based on their types (Fig.~\ref{fig:base}).
% Rather than mutating original values, it copies them, applies transformations on the copies, and returns copies to the caller:
% 
% % Listing~\ref{core-tx} presents a simplified core of the language.
% 
% \begin{itemize}
% \item
%   \emph{function} values are wrapped by a closure that forwards arguments to the original function if allowed to do so.
% \item
%   \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values.
% \item
%   \emph{primitive} values are copied unmodified and wrapped with an access interposition mechanism.
% \end{itemize}

Direct field accesses, such as assignments, require custom detection upon dereference.
To achieve this, \sys wraps fields with an interposition mechanism;
  this mechanism essentially treats direct field accesses as function calls (see \S\ref{impl} for implementation details and \S\ref{reqs} for equivalents in other environments).
% Examples of such mechanisms include \ttt{Proxy} objects (JavaScript), metatables (Lua), metaclasses (Python), and direct-accessor metaprogramming (Ruby).
\sys's wrappers detect and record changes to any of the object's fields, transforming values as needed.
For example, if a field in a transformed object is assigned a new value, that value itself has to be be transformed before being attached to the \fixme{tree}.

\sys allows toggling analyses on/off, changing analysis, or chaining multiple analysis during the execution of the program.
To achieve this, it maintains a handle to the root of both the unprocessed and the newly processed values, for further processing:
  the unprocessed value is used to create objects, at runtime, that run a different analysis;
  the new value is used to revoke or chain analyses, a feature not explored further in this paper.

\heading{Context Transformation}
To be able to track an analysis at the library boundary, \sys needs to provide each library with values that are augmented with interposition wrappers---and do this for all of the names a library to which a library has access.

To achieve this, \sys first needs to prepare a transformed copy of the library's outer context.
Semantically, the context is a map from variable names to their values.
Thus, \sys creates an auxiliary hash table mapping names to transformed values.
Names correspond to any name that, by the language definition, is accessible by the library and resolves to a value outside that library, such as globals, built-ins, module-locals, \etc.
Transformed values are created by applying the base transformation \ttt{BT} over values in the context, adding the provided analysis hooks.

%% FIXME: 
%% While user-defined global variables are stored in well-known locations,\footnote{
%%   For example, \ttt{globals} in JavaScript and \ttt{\_G} in Lua.
%% } traversing the global scope for built-in values is generally not possible.
%% To solve this problem, \sys collects such values by resolving well-known names hard-coded in a list;
%%   different lists exist for different environments and versions of the language.
%% Using this list, \sys creates a list of pointers to unmodified values. % upon startup.

Care must be taken with library-local variables. % that refer to library-specific information such as \ttt{\_\_name\_\_} in Python~\sx{bg1}.
These are accessible from anywhere within the scope of a library (similar to global variables), but resolve to a different value for each library.
Examples include the library's absolute filename, its \ttt{export}ed values, and whether the library is invoked as the application's \ttt{main} library~\sx{bg1}.
Attempting to access library-local variables directly from within \sys's scope will fail subtly, as they will end up resolving to library-local values of \sys \emph{itself}---and specifically, the module within \sys that is applying the transformation.
\sys solves this problem by leaving the value empty and deferring binding for later from within the scope of the library (see below).

\heading{Context Linking}
To link the library with the newly transformed version of its context, \sys wraps the library---still an uninterpreted string of source code---with a closure.
The closure's body starts with a prologue of the form:
\begin{verbatim}
  local pint = ctx.print
  local error = ctx.error
  ...
\end{verbatim}
These statements shadow global variable names by redefining them as local ones.
The closure accepts an argument \ttt{ctx}, which will be the customized context created earlier, assigning its entries to their respective variable names.
The prologue executes before everything else in the library.
% When the closure is applied to the customized context, the library's return value is recovered in a side-effectful manner (as in the unmodified library system) by reading the library's \ttt{exports} variable---that is, the closure does not end with an explicit \ttt{return}.
This technique leverages lexical scoping to inject a non-bypassable step in the variable name resolution process.
Instead of resolving to variables in the context, resolution will first ``hit'' library-local values augmented with analysis monitors.

Late-bound, library-local variables mentioned during context creation are the result of applying \fixme{\ttt{BT}} over variable names in the current scope;
  these names are now bound to the correct library-local values.

\heading{Library Interface Transformation}
Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
The goal of the final transformation is to track activity at the boundary;
  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.

The final transformation is applied for every new consumer of the library.
This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.

\subsection{Re-assembly}
\label{three}

To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
The central mechanism for resolution is the library cache.

To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
A context transformation is applied at most a few times (usually only once), whereas a return-value transformation is applied on every \ttt{import}.
Thus, the first level is indexed by library identifiers (as before); the second by context analysis; and the third by analysis of the \ttt{export}ed interfaces.
% The first level is indexed by library identifiers as before, the second level is indexed by implicit segments, and the third level is indexed by explicit segments.
For each library, the second level contains a collection of entries corresponding to mostly-transformed libraries, and the third level contains fully transformed libraries.
Mostly-transformed libraries have gone through the entire transformation pipeline except for the last stage:
  they have been interpreted and have had their context transformed and linked, but their return value has not been processed to track analysis of its interface.

% A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
It then applies a transformation to the library's return value.
New libraries are inserted into the second-level cache right after evaluation of the interpreted function.

\section{Implementation of Dialysis for SSJ}
\label{impl}

\begin{figure*}[t]
\centering
\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
\vspace{-2mm}
\caption{
  \textbf{Example transformations.}
   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
\fixme{No UX!}
}
\label{fig:tx2}
\vspace{-2mm}
\end{figure*}

This section details our implementation of \sys for server-side JavaScript (SSJ) in about 1.5K lines of code on top of version 8.9.4 of the Node.js runtime.
We start with the internals of \sys's Node.js implementation~\sx{impl1}, and then describe the three analyses built on \sys~\sx{impl2}.
We postpone discussion of how other environments diverge from JavaScript for later~\S\ref{reqs}.

In practice, the aforementioned dialysis stages can be implemented in two different ways.
The first is to implement \sys as a modified version of the runtime (\eg \sys-powered JavaScript) in which several stages of its library-loading facility have been augmented in-place with the techniques described earlier.
The second approach is to implement as a third-party library (\eg the \ttt{lya} package) available by the language's package manager.

With both approaches, \sys feels to users as a backward-compatible, drop-in replacement of SSJ's module system---but the second approach has several benefits.
It does not require \sys's users to add a second runtime whose sole purpose is to run analyses;
  it removes \sys's creators and maintainers from the critical path of updates between the runtime developers and its users; 
  and it simplifies \sys's evaluation and comparison with the vanilla runtime (both in terms of performance and correctness).
% However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
%   we expand on in the discussion section~\sx{reqs}.

% It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.

\subsection{System Implementation}
\label{impl1}

Node.js' module system is implemented entirely in JavaScript.
It exposes \ttt{require}, a global-looking function for importing modules.
At a high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:
(1) Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
(2) Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
(3) Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
(4) Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
(5) Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.

@@

% \begin{verbatim}
% let lib = `
%  function (exports, require, module,
%            __filename, __dirname, CTX) {
%    let Math = CTX.Math
%    let console = CTX.console
%    //...[more definitions]
%    ${moduleSource}
%  });`;
% \end{verbatim}

@@

% get second argument, no need to pass arguments around, tricky to 
% carefull hardcoding of paths, because \sys's code itself is split into modules
% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
% This is useful, for example, when...
% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;

%% TODO: implementation
%% The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
%% These skeletons provide hooks for end-developers writing analyses.
%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
%% These hooks are then extended or rewritten by developers to

Fig.~\ref{fig:tx2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
The precise wrappers depend on the intended analysis, reviewed next.

\subsection{Individual Analyses}
\label{impl2}

Individual analysis are implemented using a set of templates that provide initial constructs (see below).
\sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
As a result, code that is specific to individual analyses averages about 20--30 lines.

\heading{Security Analysis}
To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy for analyzing accesses.
The language of the analysis is given in the following grammar:

\begin{alltt}
  str:  <identifier in JS>
  libs: [ str ]
  path: str `.` path
  mode: P{ R | W | X }
  body: { [ path: mode ]: path \(\in\) mods}
  analysis:  mods body
\end{alltt}

\heading{Performance Diagnosis}

\begin{equation}
\label{eq:2}
R_{new} =
\begin{cases}
  R +1, & \varrho\times\sum_{i=1}^t{w_il_i} > \delta + \delta_0  \\
  R -1,  & \varrho\times\sum_{i=1}^t{w_il_i}  < \delta + a * \delta_0
\end{cases}
\end{equation}

Scale-in (\ie $-1$) might not seem as important, but constrained environments benefit from quick re-allocation.
However, after scale-in, the system often ends up just scaling out the same module.
To avoid such oscillation, a small reclamation delay $a$ increases the system's confidence that the workload has moved away from a specific pattern.

% ATTRIBUTION
Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency
% \eat{ is \ttt{A}-internal and how much}
comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.

\heading{Invariant Discovery}
Describe specific type system

% \subsection{Limitations}
% 
% % FIXME: Talk about the inability to 
% A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
% This is because \sys cannot transform the context of that file
% As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
% The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).

\section{Evaluation}
\label{eval}

@@

Experiments were run on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
In terms of software, we used Docker version 18.09.7 running \fixme{a minimal Ubuntu XXX version}, Jalangi \fixme{vXXX}, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
We run our software experiments within a Docker container to simplify the setup of the Jalangi framework.

>>>>

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

@@

Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
  instead of simply locating a library in the filesystem and loading it, it yields control to \sys which applies a series of transformation steps to libraries, with the goal of interposing at their boundaries.
We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
We next describe each one of these steps in more detail~(\S\ref{one}--\ref{three}).

@@

% FIXME: add user data
At a high level, the goal of program dialysis is to \fra the program at the boundaries of third-party modules, apply transformations that insert analysis-specific machinery, and then carefully \ass individual components to maintain the original semantics.
 In more detail, these three phases are as follows:

@@

Program runtime transformations such as the ones applied in the second phase are used pervasively throughout \sys.

% , such as an object returned from a module or an exception about to be sent across the network.
Transformations can be applied to any value in the language. 
The most general value is an object, a bag of records holding key-value fields;
  other value types include primitives, functions, and booleans.
% Listing~\ref{core-tx} presents a simplified core of the language.
Transformations walk objects from their root, processing component values based on their types (Fig.~\ref{fig:txfm}).
More specifically,
  (i) \emph{function} values are wrapped by closures specific to the goal of the transformation; % on the function's arguments and return values;
  (ii) \emph{object} values are recursively transformed, with their getter and setter methods replaced similar to function values; % and at times combining return results; and
  (iii) \emph{primitive} values are either transformed directly or copied unmodified and wrapped with an access interposition mechanism.
% Usually transformations do not mutate original values, but first copy them, apply transformations to the copies, and return copies to the caller.

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
  }
}
\label{fig:base}
\end{figure}

The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
These skeletons provide hooks for end-developers writing analyses.
Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
These hooks are then extended or rewritten by developers to

For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
The wrappers depend on the intended goal:
  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.

\subsection{Disassembly}
\label{one}

@@

\subsection{Reassembly}
\label{three}

% \section{Applications of Analysis}
% \label{apps}

\section{Implementation: Lya}
\label{impl}

We implemented \sys for version 8.9.4 of the Node.js runtime.
Node.js is a runtime that bun

in about 1.5K lines of JavaScript.
We summarize where other implementations would diverge in table 1

Individual analysis are implemented using a set of templates that provide initial constructs (see below).
The difference between them, \ie the amount of code that is unique to each analysis, is about 20--30 lines.

The following subsections outline how module systems handle modules at runtime, by exemplifying the internals of Node.js.
It sketches the Node.js runtime~\sx{a}, the use of the module system~\sx{b}, and the internals of how module loading works~\sx{c}.

In practice, the aforementioned dialysis stages can be implemented in two different ways.
The first is as a modified version of the runtime, where 
No-op analyses correspond to the default execution
  either 
It is introduced as a backward-compatible, drop-in replacement of the language's module system.
It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.

We went with the latter approach, providing \sys as a library, to simplify its evaluation and its comparison with the vanilla runtime (both in terms of performance and correctness).
However, we have found there are significant opportunities for performance optimization and gains in development complexity by choosing the former approach;
  we expand on these at the end of this section~\sx{opportunities}.
% get second argument, no need to pass arguments around, tricky to 
% carefull hardcoding of paths, because \sys's code itself is split into modules
% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
% This is useful, for example, when...
% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;

(1) why node.js
(2) Create a table of compatibility and show individual aspects

\heading{Module System}
Node.js' module system is implemented entirely in JavaScript.
It exposes \ttt{require}, a global-looking function for importing modules.
\fixme{Figure} above demonstrates the use of \ttt{require}.

% \begin{lstlisting}[language=js,mathescape,upquote=true]
% // -------------- [./main.js] -------------
% // importing point
% let Point = require("./point.js");
% Point.create(1, 1).print(); // => [1, 1]
% 
% // -------------- [./point.js] ------------
% let Point = function Point (x, y) {
%     this.x = x; this.y = y;
% };
% Point.prototype.print = function print () {
%   console.log([this.x, this.y]);
% };
% module.exports = {
%     create:  function create (x, y) {
%         return new Point(x, y);
%     }
% };
% \end{lstlisting}

In the example above, the main module (\ttt{main.js}) imports the \ttt{point.js} module using the \ttt{require} statement (line 3)
Functionality from the exporting module (\ttt{point.js}) that is expected to become available to the importing module (\ttt{main.js}) is assigned to a special \ttt{module.exports} object (line 13);
  the rest is module-private functionality.
Files and modules are in one-to-one correspondence (each file is treated as a separate module).
Method \ttt{require} is synchronous (\ie blocking):
  it will block execution until the module specified is loaded.
% ---and can be used to load built-in modules such as \ttt{http} and \ttt{fs}.
The module system is implemented in the \ttt{module} built-in module~\sx{c}, which locates, wraps, compiles, and executes the specified file.

\sys hooks into \ttt{module} and alters the return value of the \ttt{require} call that imports \ttt{point.js} (line 3).

\subsection{Implementation of the Module System}
\label{c}

\begin{figure*}[t]
\centering
\includegraphics[width=0.99\textwidth]{./figs/lya_ex.pdf}
\vspace{-2mm}
\caption{
  \textbf{Example transformations.}
   Applying runtime transformations (b) and context rebinding (c, d) on a simple \ttt{Math} object~\cf{impl}.
}
\label{fig:tx2}
\vspace{-2mm}
\end{figure*}

At a very high level, loading a fresh module with \ttt{require("foo");} corresponds to the following five stages:

\begin{enumerate}
% \def\labelenumi{\arabic{enumi}.}
\item Resolution: identify the file to which the module specified corresponds, and locate it in the filesystem.
\item Loading: depending on the file type, use the corresponding loader (\eg V8 compiler for \ttt{js}, \ttt{JSON.parse} for \ttt{json} \etc).
\item Wrapping: wrap the module so that module-globals get encapsulated and Node.js globals (\eg \ttt{require}) get resolved.
\item Evaluation: evaluate the wrapped module in the current context, so that global names and top-level objects get resolved correctly.
\item Caching: add the module to a handful of module-related cache structures, for purposes of consistency and performance.
\end{enumerate}

@@

% \begin{lstlisting}[language=js,mathescape,upquote=true]
% // Node.js will wrap a module with a function,
% // so as to bring certain names into scope
% // before compiling/evaluating code.
% let wrapped = "function (" +
%         "exports, require, module, " +
%         "__filename, __dirname, CTX) {" +
%     "let Math = CTX.Math" +
%     "let console = CTX.console" +
%     //...[more definitions]
%     moduleSource +
%   "});"
% \end{lstlisting}

@@

% \begin{lstlisting}[language=js,mathescape,upquote=true]
% //Input: module ID e.g., absolute filepath
% let load = function (ID) {
%   if (cache[ID]) {
%      return cache[ID];
%   }
%   let m = {
%     exports: {}, id: ID, dir: path.resolve(ID)
%   };
%   let cm = v8.compile(wrapped);
%   let ii = iris.getImplicit(ID);
%   let c = iris.freshContext(ii);
%   cm(m.exports, this.require, m, ID, m.dir, c);
%   let ei = iris.getExplicit(ID);
%   m.exports = iris.wrap(m.exports, [ei] );
%   cache[ID] = m;
%   return m.exports;
% }
% \end{lstlisting}

The \ttt{load} method in the \ttt{Module} module combines evaluation (line 10) and caching (line 14) of the wrapped module.
After evaluation, invoking the compiled function generates the value that is assigned to \ttt{module.exports} from within the module (line 12).
\sys passes a freshly constructed context at that invocation, modified according to the implicit segment of the (PIC??) corresponding to the module being loaded.
Before returning the value of \ttt{module.exports}, \sys transforms it according to the explicit segment of the (PIC??) corresponding to the module being loaded.
Finally, the results of the entire process are placed into the module cache for later use.

\subsection{Limitations}

% FIXME: Talk about the inability to 
A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
This is because \sys cannot transform the context of that file
As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).

\section{Evaluation and Experience}
\label{eval}

@@

Experiments were run on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
In terms of software, we used Docker version 18.09.7 running \fixme{a minimal Ubuntu 14.04.6 version}, Jalangi \fixme{v2}, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
We run our software experiments within a Docker container to simplify the setup of the Jalangi framework.
